Manuscript progress report

### 2024-02-16 Docs/manuscript.tex
update figures

\title{Manuscript progress report}
\author{Ying Jin}
\date{2024-02-06}

@@

  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{eta\_i, }\AttributeTok{col =} \StringTok{"True"}\NormalTok{))}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.2}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.2"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.4}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.4"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.6}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.6"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.8}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.8"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}

@@

  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{eta\_i, }\AttributeTok{col =} \StringTok{"True"}\NormalTok{))}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.2}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.2"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.4}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.4"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.6}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.6"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.8}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.8"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}

@@

\NormalTok{rand\_id }\OtherTok{\textless{}{-}} \FunctionTok{sample}\NormalTok{(}\FunctionTok{unique}\NormalTok{(pred\_nhanes\_adglmm}\SpecialCharTok{$}\NormalTok{id), }\DecValTok{4}\NormalTok{)}
\NormalTok{cols }\OtherTok{\textless{}{-}}\NormalTok{ cols[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{3}\NormalTok{]}
\FunctionTok{names}\NormalTok{(cols) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"6am"}\NormalTok{, }\StringTok{"12pm"}\NormalTok{, }\StringTok{"6pm"}\NormalTok{)}

@@

\NormalTok{  pred\_nhanes\_fgfpca }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method=}\StringTok{"fGFPCA"}\NormalTok{),}
\NormalTok{  pred\_appl\_gfosr\_l5 }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=5)"}\NormalTok{),}
\NormalTok{  pred\_appl\_gfosr\_l1 }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=1)"}\NormalTok{),}
\NormalTok{  pred\_nhanes\_adglmm }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GLMMadaptive"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}

@@

  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred360, }\AttributeTok{col =} \StringTok{"6am"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred720, }\AttributeTok{col =} \StringTok{"12pm"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred1080, }\AttributeTok{col =} \StringTok{"6pm"}\NormalTok{), }\AttributeTok{linetype=}\StringTok{"dashed"}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}

@@

@@

>>>>

\title{Manuscript progress report}
\author{Ying Jin}
\date{2024-02-16}

@@

  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{eta\_i, }\AttributeTok{col =} \StringTok{"True"}\NormalTok{), }\AttributeTok{linetype =} \StringTok{"dashed"}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.2}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.2"}\NormalTok{), }\AttributeTok{na.rm=}\NormalTok{T, }\AttributeTok{linewidth =} \FloatTok{1.0}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.4}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.4"}\NormalTok{), }\AttributeTok{na.rm=}\NormalTok{T, }\AttributeTok{linewidth =} \FloatTok{1.0}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.6}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.6"}\NormalTok{), }\AttributeTok{na.rm=}\NormalTok{T, }\AttributeTok{linewidth =} \FloatTok{1.0}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.8}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.8"}\NormalTok{), }\AttributeTok{na.rm=}\NormalTok{T, }\AttributeTok{linewidth =} \FloatTok{1.0}\NormalTok{)}\SpecialCharTok{+}

@@

  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{eta\_i, }\AttributeTok{col =} \StringTok{"True"}\NormalTok{), }\AttributeTok{linetype =} \StringTok{"dashed"}\NormalTok{)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.2}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.2"}\NormalTok{), }\AttributeTok{linewidth=}\DecValTok{1}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.4}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.4"}\NormalTok{), }\AttributeTok{linewidth=}\DecValTok{1}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.6}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.6"}\NormalTok{), }\AttributeTok{linewidth=}\DecValTok{1}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{t, }\AttributeTok{y=}\NormalTok{pred0}\FloatTok{.8}\NormalTok{, }\AttributeTok{col =} \StringTok{"0.8"}\NormalTok{), }\AttributeTok{linewidth=}\DecValTok{1}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# redefine color scale}
\NormalTok{cols }\OtherTok{\textless{}{-}}\NormalTok{ cols[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{3}\NormalTok{] }
\FunctionTok{names}\NormalTok{(cols) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"6am"}\NormalTok{, }\StringTok{"12pm"}\NormalTok{, }\StringTok{"6pm"}\NormalTok{)}

\CommentTok{\# selct four subjects}
\NormalTok{plot\_id }\OtherTok{\textless{}{-}} \FunctionTok{sort}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{68959}\NormalTok{, }\DecValTok{68624}\NormalTok{, }\DecValTok{64198}\NormalTok{, }\DecValTok{80517}\NormalTok{))}

\CommentTok{\# figure}

@@

\NormalTok{  pred\_nhanes\_fgfpca }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ plot\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method=}\StringTok{"fGFPCA"}\NormalTok{),}
\NormalTok{  pred\_appl\_gfosr\_l5 }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ plot\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=5)"}\NormalTok{),}
\NormalTok{  pred\_appl\_gfosr\_l1 }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ plot\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GFOSR (L=1)"}\NormalTok{),}
\NormalTok{  pred\_nhanes\_adglmm }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ plot\_id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mutate}\NormalTok{(}\AttributeTok{method =} \StringTok{"GLMMadaptive"}\NormalTok{)) }\SpecialCharTok{\%\textgreater{}\%}

@@

  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred360, }\AttributeTok{col =} \StringTok{"6am"}\NormalTok{), }\AttributeTok{linewidth=}\DecValTok{1}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred720, }\AttributeTok{col =} \StringTok{"12pm"}\NormalTok{), }\AttributeTok{linewidth=}\DecValTok{1}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred1080, }\AttributeTok{col =} \StringTok{"6pm"}\NormalTok{), }\AttributeTok{linewidth=}\DecValTok{1}\NormalTok{, }\AttributeTok{na.rm=}\NormalTok{T)}\SpecialCharTok{+}

@@

The fGFPCA prediction conditional on observation up to 6am looks
identical across subjects. This is not due to coding issue. In fact, if
we look at individual tracks, out of 3506 subjects there are 1473 unique
predicted tracks. There is a high change the selected four subjects all
have the same predicted tracks.

PS number of unique predicted tracks is: - 3456 when conditional on 12
pm - 3488 when conditional on 6pm

I think this is closedly determined by the variety of observed outcome
across individuals. When conditioning on 6am, there are 1475 unique
observed tracks; and 3465 and 3488 respectively when obesrved up to 12pm
and 6pm. As we see, these numbers are very close to the number of unique
prediction tracks in fGFPCA.

I'd note that the four randomly selected subjects from the last report
happen to have exactly the same observations from 0-6am. That is why
they also have identical prediction after 6am. Therefore, in this report
I arbitrarily assigned subjects to be displayed: 62161, .

In addition: - For GFOSR (L5), number of unique predicted tracks are 31,
32, 32 - For GFOSR (L1), number of unique predicted tracks are 2, 2, 2 -
For GLMMadaptive, number of unique predicted tracks are 294, 712, 1533.

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{length}\NormalTok{(}\FunctionTok{unique}\NormalTok{(pred\_nhanes\_adglmm}\SpecialCharTok{$}\NormalTok{id))}
\NormalTok{pred\_nhanes\_fgfpca }\SpecialCharTok{\%\textgreater{}\%}
  \CommentTok{\# filter(id \%in\% rand\_id) \%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(id, sind, Y) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(sind }\SpecialCharTok{\textless{}=}  \DecValTok{360}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ sind, }\AttributeTok{values\_from =}\NormalTok{ Y, }\AttributeTok{names\_prefix =} \StringTok{"sind"}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{distinct}\NormalTok{(., }\FunctionTok{pick}\NormalTok{(}\FunctionTok{starts\_with}\NormalTok{(}\StringTok{"sind"}\NormalTok{)), }\AttributeTok{.keep\_all =}\NormalTok{ T) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(id) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{t}\NormalTok{() }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{sample}\NormalTok{(., }\AttributeTok{size =} \DecValTok{4}\NormalTok{)}

  \CommentTok{\# ggplot(aes(x=sind, y=pred360, col = as.factor(id), group = as.factor(id)))+}
  \CommentTok{\# geom\_line()}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{pred\_nhanes\_fgfpca }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(id, sind, pred360) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(sind}\SpecialCharTok{\textgreater{}}\DecValTok{360}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{()}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred360, }\AttributeTok{col =} \FunctionTok{as.factor}\NormalTok{(id)), }\AttributeTok{show.legend =}\NormalTok{ F)}

\NormalTok{pred\_nhanes\_fgfpca }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(id, sind, pred720) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(sind}\SpecialCharTok{\textgreater{}}\DecValTok{720}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{ggplot}\NormalTok{()}\SpecialCharTok{+}
  \FunctionTok{geom\_line}\NormalTok{(}\FunctionTok{aes}\NormalTok{(}\AttributeTok{x=}\NormalTok{sind, }\AttributeTok{y=}\NormalTok{pred720, }\AttributeTok{col =} \FunctionTok{as.factor}\NormalTok{(id)), }\AttributeTok{show.legend =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df\_nhanes }\OtherTok{\textless{}{-}} \FunctionTok{read\_rds}\NormalTok{(}\FunctionTok{here}\NormalTok{(}\StringTok{"Data/nhanes\_bi.rds"}\NormalTok{))}
\NormalTok{df\_nhanes }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{select}\NormalTok{(SEQN, Z, sind) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(SEQN }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{filter}\NormalTok{(sind }\SpecialCharTok{\%in\%} \DecValTok{356}\SpecialCharTok{:}\DecValTok{360}\NormalTok{) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ sind, }\AttributeTok{values\_from =}\NormalTok{ Z) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{SEQN) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{distinct}\NormalTok{(.)}

\NormalTok{pred\_appl\_gfosr\_l5 }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{filter}\NormalTok{(id }\SpecialCharTok{\%in\%}\NormalTok{ rand\_id) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{select}\NormalTok{(id, sind, pred360) }\SpecialCharTok{\%\textgreater{}\%}
  \FunctionTok{pivot\_wider}\NormalTok{(}\AttributeTok{names\_from =}\NormalTok{ sind, }\AttributeTok{values\_from =}\NormalTok{ pred360) }\SpecialCharTok{\%\textgreater{}\%} 
  \FunctionTok{select}\NormalTok{(}\SpecialCharTok{{-}}\NormalTok{id) }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{distinct}\NormalTok{(.)}
\end{Highlighting}
\end{Shaded}
